The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 paper.tex
Neighbourhood Authorithy -> neighborhood authority

		Instead of the directory servers, it uses a DHT and a new Neighbourhood Authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

		The Myrmic DHT runs on top of Kademlia, and introduces the Neighbourhood Authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The Neighbourhood Authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers. This does not solve the trust issue, but it does solve the scalability issue.

>>>>

		Instead of the directory servers, it uses a DHT and a new neighbourhood authority. The DHT is a combination of Kademlia DHT and Myrmic DHT. Kademlia DHT was chosen because it is already widely used and it has proven itself for a large number of users.

		The Myrmic DHT runs on top of Kademlia, and introduces the neighbourhood authority. This authority issues certificates to nodes that participate in the DHT, but it does not participate in the DHT itself. The neighbourhood authority makes this solution not a fully decentralized one, but its role is a lot smaller than the current directory servers. This does not solve the trust issue, but it does solve the scalability issue.
